---
title: 'Consensus Community Detection'
output: rmarkdown::html_vignette
description: >
  Typical use of Consensus Community Detection package.
vignette: >
  %\VignetteIndexEntry{Consensus Community Detection}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---
 

```{r setup, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
options(tibble.print_min = 4, tibble.print_max = 4)
```

# introduction
This vignette shows the typical usage of the CCD library.

## installation
the library can be downloaded and installed from GitHub https://github.com/fabio-morea/CCD


```{r load library, message=FALSE, warning=FALSE}
library(devtools)  
install_github("fabio-morea/CCD")
library(CCD)
library(igraph)
library(tidyverse)
```


The package contains two sample networks: `roc45bc` and `roc84bc`.

## example of community detection


```{r c1, echo=TRUE}
comm <- consensus_community_detection(roc45bc,
                              t=100, 
                              method='LV', 
                              gamma_lim = 0.6) 
```
Plotting results focused on communities
```{r c1p}
plot(comm,roc45bc )

```

Plotting results focused on uncertainty (gamma coefficient).

```{r c1p1}
plot(roc45bc, vertex.color = if_else(comm$gamma > .01,"red", "green"))
```


Second example: a larger network. 
```{r c2, echo=TRUE}
comm <- consensus_community_detection(roc84bc,
                              t=100, 
                              method='LV', 
                              gamma_lim = 0.6)
comm$gamma
plot(comm, roc84bc)
plot(roc84bc, vertex.color = if_else(comm$gamma > .01,"red", "green"))

```


 